Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/appendix.tex
minor changes

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
  \begin{equation}
    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
  \end{equation}\mtodo{Prove other direction}
\end{lemma}
\begin{proof}
  By induction on the length of the execution trace.

@@

    The same reasoning applies to the case where $e_k$ is a call-start edge.
\end{proof}

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{align*}
    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
  \end{align*}
  At the same time,
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
  \end{align*}
  This means that for each $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and for each path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$. Therefore, according to~Lemma~\ref{lem:sound3}, for each $q$, $d\in M_F(q)(\top)$. It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)=\resultIFDS(P)(n)$. 
  In other words, if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
\end{proof}

>>>>

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
  \begin{equation}
    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
  \end{equation}\mtodo{Prove other direction}
\end{lemma}
\begin{proof}
  We start by proving that if $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$, by induction on the length of the execution trace.

@@

    The same reasoning applies to the case where $e_k$ is a call-start edge.\\

    For the other direction, we will prove that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.
\end{proof}

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{align*}
    \resultIFDS(P)&=\lambda n\,.\,\mvp F(n)\\
    &=\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top).
  \end{align*}
  At the same time,
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\right\}\\
    &=\left\{d\,|\,\forall r\in R\,.\,\bigsqcap_{q\in\textsf{VP}(n)}\xi(q,\,d)(r)\ne\top_T\right\}.
  \end{align*}
  This means that for any given $d\in\backCC(\resultIDE(\transCC R(P)))(n)$ and path $q\in\textsf{VP}(n)$, $\xi(q,\,d)\ne\top_T$. Therefore, according to~Lemma~\ref{lem:sound3}, $d\in M_F(q)(\top)$. It follows that $d\in\bigsqcap_{q\in\textsf{VP}(n)}M_F(q)(\top)$, which is equal to $\resultIFDS(P)(n)$. 
  Hence, we have shown that if $d\in\backCC(\resultIDE(\transCC R(P)))(n)$, then $d\in\resultIFDS(P)(n)$.
\end{proof}
